---
title: "Assignment V: GitHub and the ticketmaster.com API (R)"
subtitle: "Data Science Project Management (DS400) | Winter Term 2022/23"
author: "Submitted by Jakob Zgonc (6293178)"
date: "Submitted on `r format(Sys.time(), '%d.%m.%Y')`"
output:
  bookdown::html_document2:
    toc: yes
    number_sections: TRUE
    toc_float:
      collapsed: yes
---

```{r setup, include = F}
options(scipen=999)

knitr::opts_chunk$set(message = FALSE, warning = FALSE)

# clear work space
rm(list = ls())

```

<!-- some styling -->

```{css, echo=FALSE}

.title {font-weight: bold}

.author {padding-top: 50px;}

.author, .date {
  color: #708090;
  font-size: 17px;
  font-style: italic;
}

h1 {margin-top: 35px}

div.task {
  background-color:#DAE3F3;
  color: #337AB7; /*  #002060;*/
  border-radius: 10px; 
  padding: 20px;
  margin-top: 20px;
  margin-bottom: 20px;
  margin-left: 0px;
  margin-right: 0px;
  font-size: 15px;
  border-left: 10px solid #337AB7;

}

body .main-container {
  max-width: 1280px;
}

```

***

<br>

#### **Code of conduct**{.unnumbered}
*I hereby acknowledge that the submitted assignment is my own work. During the preparation of this assignment I have worked together with Max Mohr and Felix Koehn.*

***

This document is also available in [this GitHub repository](https://github.com/jzgonc/dspm_2022_assignment_5).

# Interacting with the API - the basics

<div class="task">
7. Perform a first `GET` request, that searches for event venues in Germany (`countryCode = "DE"`). Extract the content from the response object and inspect the resulting list. Describe what you can see.
</div>

```{r libraries}

# load libraries
library(httr)
library(tidyverse)
library(rlist)
library(kableExtra)

```

```{r func_print_df}

# function to display a data frame more appealingly
print_df <- function(df, n = 10, scrollbox = FALSE) {
  
  # styling
  df_formatted <- df %>% 
    head(n = n) %>% 
    kbl() %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 
  
  # scrollbox
  if (scrollbox) {
    df_formatted <- df_formatted %>%  
    scroll_box(width = "100%")
  }
  
  # show data frame
  df_formatted
}

```

```{r apikey}

# get API key
apikey <- readLines("ticketmaster_api_key.txt", warn = FALSE)

```

```{r url}

# url for venues
url <- "https://app.ticketmaster.com/discovery/v2/venues"

```

```{r first_apicall}

# define params for API call
params <- list(apikey = apikey, countryCode = "DE")

# get response from API and extract content
venues_DE_first_page <- GET(url = url, query = params) %>% content()

# show response
venues_DE_first_page

```

The response of the API call is a nested list. On the first level there are three items:

* `_embedded` contains the actual data we have requested. The value is a list itself. In this list, again, there is a list with all returned venues (each of which is a list, again)
* `_links` contains the url that was used for the API call (excluding the apikey and the domain). In addition, it contains the urls for the first, next and last page.
* `page` contains information about the returned page from the data source

<div class="task">
8. Extract the `name`, the `city`, the `postalCode` and `address`, as well as the `url` and the `longitude` and `latitude` of the `venues` to a data frame. This data frame should have the following structure:
```
## Rows: 20
## Columns: 7
## $ name       <chr> "Gruenspan", "Huxleys Neue Welt", "Kleine Olympiahalle", "Z~
## $ city       <chr> "Hamburg", "Berlin", "Munich", "Emmelshausen", "Mülheim", "~
## $ postalCode <dbl> 22767, 10967, 80809, 56281, 45479, 76646, 68766, 44263, 542~
## $ address    <chr> "Grosse Freiheit 58", "Hasenheide 107 – 113", "Spiridon-Lou~
## $ url        <chr> "http://www.ticketmaster.de/venue/287155", "http://www.tick~
## $ longitude  <dbl> 9.958075, 13.421380, 11.550920, 7.556560, 6.874710, 8.59908~
## $ latitude   <dbl> 53.55188, 52.48639, 48.17543, 50.15544, 51.42778, 49.12692,~
```
</div>

```{r func_simplify_list}

simplify_list <- function(l) {
  #' Simplify list
  #' 
  #' @description This function simplifies the list returned from the request
  #' by extracting relevant information for a single venue.
  #' 
  #' @param l list. The list that contains all returned information on a single
  #' venue
  #' 
  #' @return The simplified list with the relevant information
  
  l_simplified <- list(
    name = l$name,
    city = l$city$name,
    postalCode = l$postalCode,
    address = l$address$line1,
    url = l$url,
    longitude = l$location$longitude,
    latitude = l$location$latitude
  )
  
  return(l_simplified)
  
}

```

```{r first_page_df}

# apply function to each venue and stack in a data frame
lapply(venues_DE_first_page[["_embedded"]][["venues"]], simplify_list) %>% 
  list.stack() %>% 
  print_df()

```

# Interacting with the API - advanced

<div class="task">
9. Have a closer look at the list element named `page`. Did your `GET` request from exercise (7) return *all* event locations in Germany? Obviously not - there are of course much more venues in Germany than those contained in this list. Your `GET` request only yielded the first results page containing the first 20 out of several thousands of venues. Check the API documentation under the section [Venue Search](https://developer.ticketmaster.com/products-and-docs/apis/discovery-api/v2/#search-venues-v2). How can you request the venues from the remaining results pages? Iterate over the results pages and perform `GET` requests for all venues in Germany. After each iteration, extract the seven variables `name`, `city`, `postalCode`, `address`, `url`, `longitude`, and `latitude`. Join the information in one large data frame. Print the first 10 rows and the shape of the resulting data frame. The resulting data frame should look something like this (note that the exact number of search results may have changed since this document has been last modified):
```
## Rows: 12,671
## Columns: 7
## $ name       <chr> "Gruenspan", "Huxleys Neue Welt", "Kleine Olympiahalle", "Z~
## $ city       <chr> "Hamburg", "Berlin", "Munich", "Emmelshausen", "Mülheim", "~
## $ postalCode <dbl> 22767, 10967, 80809, 56281, 45479, 76646, 68766, 44263, 542~
## $ address    <chr> "Grosse Freiheit 58", "Hasenheide 107 – 113", "Spiridon-Lou~
## $ url        <chr> "http://www.ticketmaster.de/venue/287155", "http://www.tick~
## $ longitude  <dbl> 9.958075, 13.421380, 11.550920, 7.556560, 6.874710, 8.59908~
## $ latitude   <dbl> 53.55188, 52.48639, 48.17543, 50.15544, 51.42778, 49.12692,~
```

</div>

```{r func_get_venues_in_country}

get_venues_in_country <- function(country_code, verbose = TRUE) {
  #' Get venues in a country
  #' 
  #' @description Get all venues from ticketmaster via it's API and convert the 
  #' response to a data frame that contains a row for each venue.
  #' 
  #' @note This functions uses the global variables `apikey` and `url`. 
  #' In order to make this function work properly, these have to be defined.
  #' 
  #' @param country_code character. The country code to be used as parameter for
  #'  the API call
  #' @param verbose boolean. Whether to print status messages to console
  #'  (default = TRUE)
  #' 
  #' @return Data frame that contains the information on all venues in the 
  #' country
  
  # define params for API calls (size parameter must be less than 500)
  params <- list(apikey = apikey, countryCode = country_code, size = 499)
  
  # first API call to get number of pages
  n_pages <- content(GET(url = url, query = params))$page$totalPages
  
  # save timestamp of when API call was completed
  time_last_apicall <- Sys.time()
  
  # preallocate vector to store single page data frames in
  single_page_dfs <- vector(mode = "list", length = n_pages)
  
  # print message
  if (verbose) {
    cat(
      paste("Starting to retrieve venues in country", country_code,
            "from", n_pages, "pages...\n")
    )
  }
  
  # loop through pages
  for (page in 1:n_pages) {
    
    # add page number to params dictionary (API starts counting at 0)
    params$page <- page - 1
    
    # make sure we do not more than 5 requests per second
    time_since_last_apicall <- Sys.time() - time_last_apicall
    Sys.sleep(max(0, 1/5 - time_since_last_apicall))
    
    # get venues list from API call response
    venues <- content(GET(url = url, query = params))$`_embedded`$venues
    
    # update timestamp of when API call was completed
    time_last_apicall <- Sys.time()
    
    # get data frame of all venues on the current page
    # and add to single_page_dfs list
    single_page_dfs[[page]] <- venues %>%
      lapply(simplify_list) %>% 
      list.stack()
    
    # print message (progress)
    percent <- page / n_pages * 100
    cat(sprintf('\rProgress: [%-50s] %d%%',
                paste(rep('#', percent / 2), collapse = ''),
                floor(percent)))
    if (page == n_pages)
      cat('\n')
  }
  
  # stack all data frames in single_page_dfs vector
  all_venues_df <- bind_rows(single_page_dfs)
  
  # convert longitude and latitude to numeric (character before)
  all_venues_df <- all_venues_df %>%
    mutate(across(c("longitude", "latitude"), as.numeric))
  
  # print message
  if (verbose) {
    cat(paste("Retrieved data for", nrow(all_venues_df), "venues.\n"))
  }
  
  # final sleep in case a new request is sent directly after executing 
  # this function
  time_since_last_apicall <- Sys.time() - time_last_apicall
  Sys.sleep(max(0, 1/5 - time_since_last_apicall))
  
  return(all_venues_df)
  
}

```

```{r get_venues_in_DE}

# call function for Germany (country_code='DE')
venues_DE <- get_venues_in_country("DE")

# show data frame (first 10 rows only)
print_df(venues_DE)

# print shape
print(dim(venues_DE))

```

# Visualizing the extracted data

<div class="task">
10. Below, you can find code that produces a map of Germany. Add points to the map indicating the locations of the event venues across Germany.
</div>

```{r func_plot_venues}

plot_venues <- function(venues_df, country, lon_lat_ranges = NULL) {
  #' Plot venues in a country
  #' 
  #' @description Plot venues in a specific country as points on a map.
  #' 
  #' @param venues_df tibble. A data frame with the venue data
  #' (longitude and latitude have to be  numeric)
  #' 
  #' @param country character. The name of the country, needed for retrieving the 
  #' base map
  #' @lon_lat_ranges list. A list that contains the ranges for longitude and 
  #' latitude to clip the data, only used if not NULL 
  #' (default = NULL)

  # filter data for longitude and latitude ranges (only if provided)
  if (!is.null(lon_lat_ranges)) {
      venues_df <- venues_df %>% 
      filter(
        longitude >= lon_lat_ranges$longitude[1],
        longitude <= lon_lat_ranges$longitude[2],
        latitude >= lon_lat_ranges$latitude[1],
        latitude <= lon_lat_ranges$latitude[2])
  }
    
  # create plot
  ggplot() +
    # map
    borders("world", country, colour = "black", fill = "grey90") +
    # venues as points
    geom_point(aes(x = venues_df$longitude, y = venues_df$latitude),
               color = "darkblue", alpha = 0.5, size = 0.5) +
    # remove ticks, labels, spines etc
    theme_void() +
    # map projection
    coord_quickmap() +
    # labels
    labs(title = paste("Event locations across", country),
         caption = "Source: ticketmaster.com") +
    # theme adjustments
    theme(title = element_text(size=8, face='bold'),
          plot.caption = element_text(face = "italic"))

}

```

```{r plot_venues_in_DE, dev='svglite'}

# call plotting function without specifiying the extreme points
plot_venues(venues_df = venues_DE, country = "Germany")

```

<div class="task">
11. You will find that some coordinates lie way beyond the German borders and can be assumed to be faulty. Set coordinate values to `NA` where the value of `longitude` is outside the range (`5.866, 15.042`) or where the value of `latitude` is outside the range (`47.270, 55.059`) (these coordinate ranges have been derived from the extreme points of Germany as listed on Wikipedia (see [here](https://en.wikipedia.org/wiki/Geography_of_Germany#Extreme_points)). For extreme points of other countries, see [here](https://en.wikipedia.org/wiki/Lists_of_extreme_points#Sovereign_states)).
</div>

```{r plot_venues_in_DE_clipped, dev='svglite'}

# call plotting function and pass extreme points
plot_venues(
  venues_df = venues_DE, 
  country = "Germany",
  lon_lat_ranges = list(
    longitude = c(5.866, 15.042),
    latitude = c(47.270, 55.059)
  )
)

```

# Event locations in other countries

<div class="task">
12. Repeat exercises (9)–(11) for another European country of your choice. (Hint: Clean code pays off! If you have coded the exercises efficiently, only very few adaptions need to be made.)
</div>



<br>

***